---
title: "RC class for Google Geooding API"
author: "Bruno Barakat"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The lab5ab package provides a RC class named `address` to use geocoding and reverse geocoding from Google API.

## Creating a address object
In order to create an object of address class, you need to give either an character address or a numeric vector of latitude or longitude. 

```{r,include=FALSE}
library(devtools)
install_github("brbatv/lab5",force=TRUE)
library(lab5ab)
address_or_coordinates<-"Paris"
```
```{r,results="hide"}

my_address<-address$new(address_or_coordinates)
````

The constructor will recognize what is the type of the argument (address or coordinates) and tell you if you give wrong inputs.

### Add special filters
You can give optional parameters to the constructor, and theses are the ones available in the google API documention. For extra reference, please see <https://developers.google.com/maps/documentation/geocoding/intro#RegionCodes> and <https://developers.google.com/maps/documentation/geocoding/intro#ComponentFiltering>

A example of use can be found below :
```{r,eval=FALSE}

my_address<-address$new("Toledo",region="ES")
my_address<-address$new("Santa Cruz",components="country:ES")
````


### Change the API key
In order to change the API key, you'll need to open utilities.R and change the key inside the `add_api_key_to_url` function. By default the key of the creator is used. 

## Getting the results in different ways
Address class has 3 fields : `$Coordinates` , `$Components` and `$Formatted_Address`

1. `$Coordinates` gives back a named numeric vector of the most precise result found by Google. 

2. `$Formatted_Address` gives back a character of all possible results found by Google.

3. `$Components` gives back a more detailed data frame on the location of the most precise result found by Google.


## Examples :
###Search by address
```{r}
#Search by address
my_address<-address$new("33 av des champs elysees Paris")
my_address$Formatted_Address
my_address$Components
my_address$Coordinates

````
### Search by coordinates
```{r}
#Search by coordinates
my_address<-address$new(c(58.39784,15.57601))
my_address$Formatted_Address
my_address$Components
my_address$Coordinates

````


